A modelling strategy to improve cacao quality and productivity

### 2021-10-12 papers/model/paper_model.tex
graficas modificadas

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2020}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

% Authors, for the paper (add full first names)
\Author{Angela Romero V $^{1,\dagger,\ddagger}$*\orcidA{}, Adriana Gallego $^{2}$ and Anyela V. Camargo R.$^{1, \ddagger}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The John Bingham Laboratory, NIAB, 93 Lawrence Weaver Road, Cambridge CB3 0LE, UK 1}\\ %e-mail@e-mail.com\\
$^{2}$ \quad BIOS Colombia}%; e-mail@e-mail.com}

@@

\section{Introduction}

Cocoa ( \textit{Theobroma cacao }L. ) is an important worldwide perennial tropical crop endemic to the South American rainforests \citep{zuidema2005, motamayor2002, argout2011, Rodriguez2019}. Cacao plant member of the Malvaceae (formerly Sterculiaceae)  botanical family such as  cotton \textit{ Gossypium hirstium} \citep{Nix2017cotton} wich is modeled in SIMPLE model \citep{Zao2019simple}. Cocoa is grown for its fruits, known as cacao pods.  \citep{ Niemenak2010, suarez2021}. Only the 5\% of the world cocoa yield is desalinated for Fine-cocoa production due to the low productivity of  the traditional crop management \citep{argout2011}.  In Colombia, cocoa  is  traditionally  consumed  as  a  beverage. It is one of the crops promoted by the Colombian government in the social and agricultural development  programs aimed at favouring peace in post-conflict regions \citep{Rodriguez2019, Abbott2019} as cocoa is grown by approximately 52.000 \citep{Gutierrez2020} and 98\% of production being carried out by small and medium-sized producers \citep{Garcia2014, Escobar2020}. Colombia registered an increase of 3.750 tons in production in 2020 compared to the previous year \citep{lamos2020}.

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Phenology of cocoa in Colombia for crop modelling.\\}} 
	\includegraphics[scale=0.3]{images/phenology.png}\\
	\footnotesize{Credits: Taken from from Dreamstime.com, phys.org \citep{toledo2021} and \cite{lopez2018}}
	\label{fig:pheno}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Daily average temperature and available photosynthetic solar radiation (PAR) conditions. \\}}
	\includegraphics[scale=0.25]{images/tempe.png}
	\includegraphics[scale=0.25]{images/SRAD.png}
	\label{fig:temp}
\end{figure}

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Precipitation and relative humidity per month in Colombia \\}}
	\includegraphics[scale=0.4]{images/rainmonth.png}
	\label{fig:rain}
\end{figure}
\newpage

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Thermal time characterization of cocoa for five locations.\\}} 
	\includegraphics[scale=0.3]{images/ttbbox.png}
	\label{fig:ttbox}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {SIMPLE model output for cocoa in Colombia.\\ }} 
	\includegraphics[scale=0.35]{images/outmodel.png}
	\label{fig:m1}
\end{figure}

\subsection{Day of harvest prediction}
\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Day of harvest cocoa simulation\\ }} 
	\includegraphics[scale=0.4]{images/RegionHarvest.png}
	\label{fig:dayH}
\end{figure}
%\begin{figure}[h!]
%	\centering
%	\caption{\footnotesize {Weather variables during flowering times.\\}} 
%	\includegraphics[scale=0.4]{images/averageS.png}
%	\label{fig:weather}
%\end{figure}

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Pearson correlation among weather variables and flowering dates all locations. \\}} 
	\includegraphics[scale=0.4]{images/heatm.png}\\
	\label{fig:heat}
	{\footnotesize thermalT= thermal time without Tb. ttb= thermal time with Tb. WS2M= Wind Speed at 2 Meters (m/s). T2MDEW = Dew/Frost Point at 2 Meters ($^\circ$C) }
\end{figure}
\newpage

>>>>

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2021}
\copyrightyear{2020}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

% Authors, for the paper (add full first names)
\Author{Angela Romero V $^{1,\ddagger}$*\orcidA{}, Adriana Gallego $^{2}$ and Anyela V. Camargo R.$^{1, \ddagger}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad The John Bingham Laboratory, NIAB, 93 Lawrence Weaver Road, Cambridge CB3 0LE, UK 1\\$^{2}$ \quad BIOS Colombia}%; e-mail@e-mail.com}

@@

\section{Introduction}
Cocoa ( \textit{Theobroma cacao }L. ) is an important worldwide perennial tropical crop endemic to the South American rainforests \citep{zuidema2005, motamayor2002, argout2011, Rodriguez2019}. Cacao plant member of the Malvaceae (formerly Sterculiaceae)  botanical family such as  cotton \textit{ Gossypium hirstium} \citep{Nix2017cotton} wich is modeled in SIMPLE model \citep{Zao2019simple}. Cocoa is grown for its fruits, known as cacao pods.  \citep{ Niemenak2010, suarez2021}. Only the 5\% of the world cocoa yield is desalinated for Fine-cocoa production due to the low productivity of  the traditional crop management \citep{argout2011}.  In Colombia, cocoa  is  traditionally  consumed  as  a  beverage. It is one of the crops promoted by the Colombian government in the social and agricultural development  programs aimed at favouring peace in post-conflict regions \citep{Rodriguez2019, Abbott2019} as cocoa is grown by approximately 52.000 \citep{Gutierrez2020} and 98\% of production being carried out by small and medium-sized producers \citep{Garcia2014, Escobar2020}. Colombia registered an increase of 3.750 tons in production in 2020 compared to the previous year \citep{lamos2020}.

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Phenology of cocoa in Colombia for crop modelling.\\}} 
	\includegraphics[scale=0.4]{images/phenology.png}\\
	\footnotesize{Credits: Taken from from Dreamstime.com, phys.org \citep{toledo2021} and \cite{lopez2018}}
	\label{fig:pheno}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.5]{images/clima.png}
	\caption{\footnotesize {Daily average temperature and available photosynthetic solar radiation (PAR) conditions. \\}}	
	\label{fig:temp}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.4]{images/rainmonth.png}
	\caption{\footnotesize {Precipitation and relative humidity per month in Colombia \\}}
	\label{fig:rain}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{images/ttbbox.png}
	\caption{\footnotesize {Thermal time characterization of cocoa for five locations.\\}} 
	\label{fig:ttbox}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.35]{images/outmodel.png}
	\caption{\footnotesize {SIMPLE model output for cocoa in Colombia.\\ }} 
	\label{fig:m1}
\end{figure}

\subsection{Day of harvest prediction}
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.4]{images/RegionHarvest2.png}
	\caption{\footnotesize {Day of harvest cocoa simulation\\ }} 
	\label{fig:dayH}
\end{figure}
%\begin{figure}[h!]
%	\centering
%	\caption{\footnotesize {Weather variables during flowering times.\\}} 
%	\includegraphics[scale=0.4]{images/averageS.png}
%	\label{fig:weather}
%\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.4]{images/heatm.png}\\
	\label{fig:heat}
	\caption{\footnotesize {Pearson correlation among weather variables and flowering dates all locations. \\}} 
	{\footnotesize thermalT= thermal time without Tb. ttb= thermal time with Tb. WS2M= Wind Speed at 2 Meters (m/s). T2MDEW = Dew/Frost Point at 2 Meters ($^\circ$C) }
\end{figure}
\newpage
